### 2017-04-13 paper/sexSelectionSpacing-ver1.tex
Edit intro part

The extent of son preference has been an important research area for 
decades and is as salient as ever.
Three approaches have been in widespread use in the literature:
birth spacing, parity progression, and sex ratio \citep{Leung1988}.
Before the availability of prenatal sex determination, parents' only choice 
if they wanted a son was to try for another pregnancy as soon as possible 
after the birth of a girl. 
In that case, son preference leads to a shorter spacing from the birth
of a daughter until the next birth   
\citep[see, for example,][]{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
The resulting shorter spacing is thought to be associated with worse 
health outcomes for the girls 
\citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.
Parents are also more likely to cease childbearing after the birth of 
a son than after a daughter, resulting in a lower parity progression
with the number of sons \citep{ben-porath76b,Das1987,Arnold1997,clark00}.

Sex ratio is the ratio of boys to girls measured for given ages, 
or, after the introduction of prenatal sex determination, at birth.
Deviation from the natural sex ratio is taken as an indication of sex preference
leading to differential mortality and/or use of prenatal sex selection.

@@

With the introduction of sex-selective abortions, parents can now abort
a fetus of unwanted sex and the use of sex selection can therefore 
directly provide us a picture of the degree of son preference.
Our understanding of the use of sex selection is, however, constrained by 
lack of information;
there are no official data on sex selection, and the few surveys that ask 
about use of sex selection show signs of serious under-reporting \citep{goodkind96}.
With no direct information, researchers have relied on a simple method for 
establishing factors that affect sex selection: use the sex of children born as 
the dependent variable, and estimate the effects of variables on the probability 
of having a son.%
\footnote{
In the absence of any interventions, the probability of having a son
is approximately 0.512, which is independent of genetic factors \citep{ben-porath76b,jacobsen99}.
With fetus sex random, a statistically significant variable indicates an association with 
use of sex-selective abortions.
Examples of studies that have used this approach are \cite{retherford03b},
\cite{jha06}, and \cite{abrevaya09}. 
}
Based on this simple method, we know that families with no sons are more likely to
use sex selection the higher the parity;
that use of sex selection increases with socioeconomic status, especially education;
and that sex selection is more widespread in cities than in rural areas 
\citep{retherford03b,jha06,abrevaya09}.%
\footnote{
There is substantial disagreement on whether sex-selective abortion is used for the 
first birth \citep{retherford03b,jha06}.
}

>>>>

The extent of son preference has been an important research area for 
decades and is as salient as ever.
Three approaches have been in widespread use in this literature:
birth spacing, parity progression, and sex ratio \citep{Leung1988}.
Before prenatal sex determination became widely available, parents' only 
option if they wanted a son was to try for another pregnancy as soon as 
possible after the birth of a girl.
A preference for sons can therefore lead to shorter spacing until next 
birth after the birth of a daughter than after the birth of a son 
\citep{Das1987,Rahman1993,Pong1994,Haughton1996,Arnold1997}.
The resulting shorter spacing is thought to be associated with worse 
health outcomes for the girls 
\citep{arnold98,Whitworth2002,Rutstein2005,Conde-Agudelo2006}.
Parents are also more likely to cease childbearing after the birth of 
a son than after a daughter, resulting in a lower parity progression
with the number of sons \citep{ben-porath76b,Das1987,Arnold1997,clark00}. 
Finally, increase in the sex ratio---the ration of boys to
girls---can serve as an indication of son preference because 
of differential mortality or underreporting \citep{sen90,sen92,Merli2000,anderson08}.

 and/or use of prenatal sex selection

or, after the introduction of prenatal sex determination, at birth.
In the absence of any interventions, the probability of having a son
is approximately 0.512, which is independent of genetic factors 
\citep{ben-porath76b,jacobsen99}.
With fetus sex random, a statistically significant variable indicates an 
association with use of sex-selective abortions \citep{retherford03b,jha06,abrevaya09}.

@@

Our understanding of the use of sex selection is, however, constrained by 
lack of information;
there are no official data on sex selection, and the few surveys that ask 
about use of sex selection show signs of serious under-reporting \citep{goodkind96}.
With no direct information, researchers have relied on a simple method for 
establishing factors that affect sex selection: use the sex of children born as 
the dependent variable, and estimate the effects of variables on the probability 
of having a son.%
\footnote{
In the absence of any interventions, the probability of having a son
is approximately 0.512, which is independent of genetic factors \citep{ben-porath76b,jacobsen99}.
With fetus sex random, a statistically significant variable indicates an association with 
use of sex-selective abortions.
Examples of studies that have used this approach are \cite{retherford03b},
\cite{jha06}, and \cite{abrevaya09}. 
}
Based on this simple method, we know that families with no sons are more likely to
use sex selection the higher the parity;
that use of sex selection increases with socioeconomic status, especially education;
and that sex selection is more widespread in cities than in rural areas 
\citep{retherford03b,jha06,abrevaya09}.%
\footnote{
There is substantial disagreement on whether sex-selective abortion is used for the 
first birth \citep{retherford03b,jha06}.
}
